### 2016-01-26 project/paper/sections/analysis.tex
Verslag enzuu

\subsection{Quality assessment}
\label{ssec:quality}
\todo[inline]{Alinea over hoe we data samen zetten. Name matching, problemen hierbij, Aantal entries in training dataset en research set, aantal positieve voorbeelden t.o.v. negatieve voorbeelden (en vermelden dat dit een probleem is en hoe we dit oplossen/compenseren), andere statistieken i.v.m. data, outliers}

>>>>

In this section we first perform an initial analysis of the data. We check their distributions and assess whether transformations should be performed for better expected results. Furthermore, we can get an initial idea of what variables will perform well by comparing the mean values for people with and without a Nobel Prize. This analysis is done using the R statistical software package.

Next, the logistic regression model is learned on the resulting dataset and evaluated using cross-validation. We experiment with excluding variables that are not relevant and balancing the number of positive and negative examples.

\subsection{Quality assessment}
\label{ssec:quality}

The merged dataset contains two variables that are \emph{fuzzy}: the number of likes on Facebook, which serves as a popularity measure, and the number of results for a specialised Google Scholar search, which serves as a productivity measure. Both might be prone to errors. Furthermore, some normalisation should be performed so that variables with a larger scale do not receive more weight in the final model. Since the university rankings are on a scale of $[0, 100]$ we will transform all variables to that scale.

\subsubsection{Popularity measure}
\label{sssec:popularity}
The popularity measure comes from gathering the number of likes on Facebook. Because this is done automatically and popular names might occur more than ones, we should check for outliers. A boxplot is shown in Figure~\ref{fig:popuInitialBox} and a density plot in Figure~\ref{fig:popuInitialDensity}. We can immediately see a problem: the outlier at 17 million deforms the distribution. It is the result for Einstein, however, and not an error in the data. Manual verification confirmed this for all seemingly high values. In order to solve this without having to remove any data, we perform a transformation using the natural logarithm. Logarithmic transformations are often used to normalise right-skewed distributions. The exact transformation is given by
\begin{equation}
\label{eq:logtransform}
t(x) = \begin{cases} ln(x), & \mbox{if } x \neq 0 \\ 0, & \mbox{if } x = 0 \end{cases}
\end{equation}
in order to correct $ln(0) = -\infty$. The same plots for the resulting distribution are given in Figures~\ref{fig:popuTransformedBox} and \ref{fig:popuTransformedDensity}. While still being far from normal, the outliers are now far less extreme. Next, the results are normalised by dividing by the maximal value and rescaled to $[0, 100]$.

In order to get an initial estimate whether it will be significant in the model, we can compare the mean value for winners and non-winners. Since there are sufficient examples, we may assume normality of sampling distributions and perform a standard two-sample $t$ test for unequal variances. The sample means are 
\begin{table}[H]
\centering
\begin{tabular}{c|c}
\textbf{\textsc{Nobel}} & \textbf{\textsc{Non-nobel}} \\ \hline
\rule{0pt}{4mm}23.05663&14.44544\\
\end{tabular}
\end{table}
Using R we find that the true means are not equal, which is what we hoped for the model.
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/popuInitialBox.pdf}
        \caption{Boxplot}
        \label{fig:popuInitialBox}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/popuInitialDensity}
        \caption{Density plot}
        \label{fig:popuInitialDensity}
    \end{subfigure}
    \caption{Distribution plots for raw popularity measure.}
\end{figure*}
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/popuTransformedBox}
        \caption{Boxplot}
        \label{fig:popuTransformedBox}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/popuTransformedDensity}
        \caption{Density plot}
        \label{fig:popuTransformedDensity}
    \end{subfigure}
    \caption{Distribution plots for transformed popularity measure.}
\end{figure*}

\subsubsection{Productivity measure}
\label{sssec:productivity}

### 2016-01-26 project/paper/sections/data.tex
Verslag enzuu

\item{\textbf{Facebook. }} As mentioned, every person on Wikipedia has an automatically generated Facebook page. Querying Facebook can be done using the Graph API with simple HTTP GET requests \cite{graphAPI}. Specialised queries can be constructed using combinations of GET parameters, for which the results are returned in JSON format. Because of this, out of all non-linked sources, information from Facebook was by far the easiest to gather. One difficulty that is worth mentioning, is the limit of consecutive queries that can be send to the Facebook Graph API.
We noticed that after sending more or less 630 queries the usertoken that is needed the retrieve the information expires. If you generate a new token you aren't allowed to immediatly start querying again. You have to wait for at least an hour. 
This is in fact an odd number of queries, if you read the documentation of the Graph API, only 200 queries per hour are allowed \cite{graphAPIlimit}.
For people with multiple pages, the number of liked for the most liked page is used. Because popular names might have pages not related to the scientist we are interested in, some results might be noisy. Such outliers have to be pruned afterwards.

\item{\textbf{Google Scholar. }} Google Scholar provides advanced search options, the most relevant for us is searching by author. In contrary to Facebook this not achieved by combining GET parameters, but by manually constructing the advanced search terms. For example, to search for publications by Albert Einstein the query  \emph{author:"Albert Einstein"} can be used. The resulting page shows the number of results, which we can then parse. Based on manual testing, Google's advanced search performs pretty well for finding only results for a given author. However, as before, people with the same name can give noisy results, so some outlier detection has to be performed. A second difficulty arose when Google appeared to block automated requests. Appendix \ref{sec:googlescholar} gives an overview of some methods we used in attempt to moderately successfully circumvent those restrictions.
\end{itemize}

>>>>

\item{\textbf{Facebook. }} As mentioned, every person on Wikipedia has an automatically generated Facebook page. Querying Facebook can be done using the Graph API with simple HTTP GET requests \cite{graphAPI}. Specialised queries can be constructed using combinations of GET parameters, for which the results are returned in JSON format. Because of this, out of all non-linked sources, information from Facebook was by far the easiest to gather.

One difficulty that is worth mentioning, is the limit of consecutive queries that can be send to the Facebook Graph API. We noticed that after sending more or less 630 queries the user token that is needed to retrieve information expires. If you generate a new token, you aren't allowed to immediately start querying again but have to wait half an hour. This number of queries is odd, the Graph API documentation states that only 200 queries per hour are allowed \cite{graphAPIlimit}.

For people with multiple pages, the number of liked for the most liked page is used. Because popular names might have pages not related to the scientist we are interested in, some results might be noisy. Such outliers have to be pruned afterwards.

\item{\textbf{Google Scholar. }} Google Scholar provides advanced search options, the most relevant for us is searching by author. In contrary to Facebook this not achieved by combining GET parameters, but by manually constructing the advanced search terms. For example, to search for publications by Albert Einstein the query  \emph{author:"Albert Einstein"} can be used. The resulting page shows the number of results, which we can then parse. Based on manual testing, Google's advanced search performs pretty well for finding only results for a given author. However, as before, people with the same name can give noisy results, so some outlier detection has to be performed. An additional difficulty arose when Google appeared to block automated requests. Appendix \ref{sec:googlescholar} gives an overview of some methods we used in attempt to moderately successfully circumvent those restrictions.
\end{itemize}
